Lattice Boltzmann study of mass transfer for two-dimensional Bretherton/Taylor bubble train flow

### 2012-12-17 Text/Final/introduction.tex
Minor-minor change.

Typical numerical studies of mass transfer
\cite{kreutzer-overview,vanbaten-circular} do not consider the simulation of
bubble shapes for $Ca>0.1$. {\color{red} The interesting work by
\citet{onea-mass} only takes into account short length bubbles in microchannels
with a square cross section. As well the Schmidt number around $0.8$ is  used
and the thickness of the concentration and momentum boundary layer is similar
leading to qualitative results.} The usual simulation of mass transfer is
performed as follows: 
\begin{description}
 \item[I] The bubble shape is calculated either
through analytical correlations \cite{bretherton} or experimental correlations
\cite{cerro-bubble-train} without directly resolving bubble shapes through
multiphase simulations.  The expressions for bubble shapes are available only
for flows with capillary number $Ca<0.1$.
  \item[II] Hydrodynamic fields
are then obtained by performing simulations of one-component flow around the
bubble by imposing the bubble velocity on the channel walls. Thus, the simulations are
performed in the reference frame moving with the bubble. A stress-free
condition is imposed at the bubble surface.
  \item[III]  The mass transfer
simulations are performed in the reference frame moving with the bubble. The
saturation concentration is imposed at the bubble surface. Only one unit cell
containing a single bubble is used for simulations. Periodic concentration boundary conditions are
utilized to determine the volumetric mass transfer coefficient, which is
calculated through the following equation \cite{vanbaten-circular}:
\begin{equation} \label{main:simulation:equation}
\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\cinoutlet\rangle}
\frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\ cell\ volume}},
\end{equation}
 where $\langle\cinoutlet(t)\rangle=\int{C \uinoutlet
\mathrm{d}A}/\int{\uinoutlet\mathrm{d}A}$ is the space-averaged inlet/outlet (periodic boundary conditions)
concentration as a function of time. Therefore, in terms of the mass transfer definition, $\langle\cinoutlet(t)\rangle$ plays the role of the 
characteristic concentration.
%This is the characteristic concentration in the definition, Eq. \ref{eq:main:definition}.  
The time-averaged
concentration flux ($\mathrm{\overline{Flux}}$) is calculated as the difference
between the overall average concentration in the whole domain
($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$) at time $t_1$ and at time
$t_2$ divided by the time difference $t_2-t_1$. The agreement between numerical
simulations \cite{vanbaten-circular} and experimental correlations of \citet{bercic-mass}
% TODO: was good where?
was good. 
 \end{description}

>>>>

Typical numerical studies of mass transfer
\cite{kreutzer-overview,vanbaten-circular} do not consider the simulation of
bubble shapes for $Ca>0.1$. {\color{red} The interesting work by
\citet{onea-mass} only takes into account short length bubbles in microchannels
with a square cross section. As well, in this work  the Schmidt number around $0.8$ is  used:
thus, the thickness of the concentration and momentum boundary layer is similar
leading to qualitative results.} The usual simulation of mass transfer is
performed as follows: 
\begin{description}
 \item[I] The bubble shape is calculated either
through analytical correlations \cite{bretherton} or experimental correlations
\cite{cerro-bubble-train} without directly resolving bubble shapes through
multiphase simulations.  The expressions for bubble shapes are available only
for flows with capillary number $Ca<0.1$.
  \item[II] Hydrodynamic fields
are then obtained by performing simulations of one-component flow around the
bubble by imposing the bubble velocity on the channel walls. Thus, the simulations are
performed in the reference frame moving with the bubble. A stress-free
condition is imposed at the bubble surface.
  \item[III]  The mass transfer
simulations are performed in the reference frame moving with the bubble. The
saturation concentration is imposed at the bubble surface. Only one unit cell
containing a single bubble is used for simulations. Periodic concentration boundary conditions are
utilized to determine the volumetric mass transfer coefficient, which is
calculated through the following equation \cite{vanbaten-circular}:
\begin{equation} \label{main:simulation:equation}
\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\cinoutlet\rangle}
\frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\ cell\ volume}},
\end{equation}
 where $\langle\cinoutlet(t)\rangle=\int{C \uinoutlet
\mathrm{d}A}/\int{\uinoutlet\mathrm{d}A}$ is the space-averaged inlet/outlet (periodic boundary conditions)
concentration as a function of time. Therefore, in terms of the mass transfer definition, $\langle\cinoutlet(t)\rangle$ plays the role of the 
characteristic concentration.
%This is the characteristic concentration in the definition, Eq. \ref{eq:main:definition}.  
The time-averaged
concentration flux ($\mathrm{\overline{Flux}}$) is calculated as the difference
between the overall average concentration in the whole domain
($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$) at time $t_1$ and at time
$t_2$ divided by the time difference $t_2-t_1$. The agreement between numerical
simulations \cite{vanbaten-circular} and experimental correlations of \citet{bercic-mass}
% TODO: was good where?
was good. 
 \end{description}
